Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-04 Arxiv/main.tex
update a bit about accuracy comparison.

\subsection{Baseline Mechanisms}
\label{subsec_baselines}
Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.

@@

\subsubsection{Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

@@

 Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:

@@

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\

@@

  \item[\textbf{case}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
  \qquad &
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}
  % we also have: 
  % \begin{align*}
  %  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
  % \qquad &
  % 1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  % \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  % \qquad &\cdot 
  % \prod_{k = 0}^{m-1}
  % \sqrt{(1 + \frac{1}{2(\alpha + k)})
  % (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  % } \\
  % \qquad & \cdot 
  % \prod_{k = 1}^{m} 
  % \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  % \geq \quad & Pr[ - t \leq Y < t + 1] \\
  % = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
  % \end{align*}
  % when $\alpha = \beta$
\end{itemize}

In both cases, $Pr[\hellinger(\bysinfer(\dataobs), r_L )^2 = 0]$ asymptotically equal to 1 when data size increases.

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
  In Beta-binomial model,
  we have following formula for accuracy:
  \begin{align}
  \label{eq_acc}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
  \end{align}
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
%   Unfolding the Hellinegr distance in this accuracy formula:
%  \begin{itemize}

>>>>

\subsection{Baseline Mechanisms}
\label{subsec_baselines}
Baseline Mechanisms are introduced in prior to our mechanism, $\hexpmech$.

@@

\subsubsection{Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism with post-processing, $\lapmech$. $\lapmech$ produces an output $r_L$:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$, a Laplace distribution with location $0$ and scale $\frac{\Delta \bysinfer}{\epsilon}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

@@

 Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, then the improved Laplace mechanism $\ilapmech$ is producing an output $r_{IL}$:

@@

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
= \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\

@@

  \item[\textbf{case}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 =
  \qquad &
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

\end{itemize}

\begin{itemize}
  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
  \item[\textbf{t = 1}]
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$. 
  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
\end{itemize}
In all cases above, probabilities are fixed whenever data size changes.

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
  In Beta-binomial model,
  we have following formula for accuracy:
  \begin{align}
  \label{eq_acc}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
  \end{align}
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\

For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.

\begin{table*}[h!]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.39346934028 & 0.39346934028 & 0.39346934028  \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 &  &  & \\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table*}

%   Unfolding the Hellinegr distance in this accuracy formula:
%  \begin{itemize}
